---
title: "p8105_hw1_qw2331"
output: github_document
---

I'm an R Markdown document! 

## Problem 1

Import necessary packages

```{r message =  FALSE}
library(tibble)
library(tidyverse)
```


Create a sequence of variables first

```{r}
set.seed(1234)

vec_numeric <-  rnorm(10)
vec_logic <-  c(vec_numeric > 0)
vec_char <-  vector("character", length = 10)
vec_factor <- factor(c("a", "a", "b", "c", "b", "c", "a", "b", "b", "c"))
```


Form a data frame using the **`tibble`** function and display

```{r}
mydataframe <-  tibble(
  vec_numeric, 
  vec_logic, 
  vec_char, 
  vec_factor)

mydataframe
```


Calculate the mean of each variable using the **`pull`** function

```{r warning = FALSE}
for (i in names(mydataframe)) {
  cat("The mean of", i, "is ", mean(pull(mydataframe, i)), "\n")
}
```


Apply the **`as.numeric`** function to the logical, character and factor variables

```{r results = "hide"}
for (i in names(mydataframe)[c(2:4)]) {
  cat("Converting", i, "to", as.numeric(pull(mydataframe, i)), "\n")
}
```


## Problem 2

Install a package containing the `penguins` dataset and load the dataset

```{r}
data("penguins", package =  "palmerpenguins")
```


A short description of the dataset:  
+ The names of this dataset are *``r names(penguins)``*
+ The size of this dataset is ``r nrow(penguins)`` rows and ``r ncol(penguins)`` columns  
+ The mean flipper length is ``r mean(pull(penguins, "flipper_length_mm"), na.rm = TRUE)``

Make a scatterplot of `flipper_length_mm` (y) vs `bill_length_mm` (x)

```{r warning = FALSE}
ggplot(penguins,
       aes(bill_length_mm, flipper_length_mm, color = species)
       ) + geom_point()
```


Export the scatter plot using **`ggsave`** function

```{r warning = FALSE}
ggsave("myplot_penguins.png")
```


